\documentclass[margin,line]{resume}

\usepackage[utf8]{inputenc}  
\usepackage[T1]{fontenc}
\usepackage{lmodern} % polices vectorielles Latin Modern (respecte + les conventions)
%\usepackage{textcomp}% symboles supplementaires
%\usepackage{aeguill} % polices Adobe

\usepackage[pdftex,                %
    bookmarks         = true,%     % Signets
    bookmarksnumbered = true,%     % Signets numerotes
    pdfpagemode       = None,%     % Signets/vignettes fermÔøΩ ÔøΩ l'ouverture
    pdfstartview      = FitH,%     % La page prend toute la largeur
    pdfpagelayout     = SinglePage, % Vue par page
    colorlinks        = true,%     % Liens en couleur
    % Pour le pdf
    linkcolor = blue, anchorcolor = blue, citecolor = green, menucolor = red, urlcolor = blue,
    % Pour l'impression
    %linkcolor = black, anchorcolor = black, citecolor = black, menucolor = black, urlcolor = magenta,
    pdfborder = {0 0 0}%   % Style de bordure : ici, pas de bordure
    ]{hyperref}%                   % Utilisation de HyperTeX

%Insertion des informations sur le document
\hypersetup{ % Modifiez la valeur des champs suivants
    pdfauthor   = {Sébastien M. Crouzet},%
    pdftitle    = {CV Sébastien M. Crouzet}}


\begin{document}
\name{\Large Sébastien Crouzet}
%\address{}

\begin{resume}

    %\hfill \textbf{ \textsl{ \large Application for a data scientist position}}
    
    \vspace{3mm}
    % Contact Information
    \section{\mysidestyle Contact\\Information}
    Weserstraße 203, 12047 Berlin, Germany            \hfill e-mail: \href{mailto:seb.crouzet@gmail.com}{seb.crouzet@gmail.com} \\
    web: \url{http://scrouzet.github.io} \hfill linkedin: \url{www.linkedin.com/in/scrouzet/}\\
    \hfill phone: +49 157 31749054 \\ 
    % \hfill fax: +33 5 62 17 28 09 \\

    \vspace{3mm}
    % Education
    \section{\mysidestyle  Academic \\ Experience\\ \& Education  }
    
  \textbf{Post-doctoral Researcher}, Charité University, Berlin, Germany \hfill \textbf{2012-2014}\\
	\textsl{Eyetracking, EEG recordings and Machine learning}
  	
	\vspace{-1.5mm}		
	\textbf{Post-doctoral Researcher}, Brown University, Providence, RI, USA \hfill \textbf{2010-2012}\\
	\textsl{Machine learning: multivariate classification and regression, Computational models of visual object recognition (performed on \href{http://www.image-net.org}{very large image datasets})}
	%\vspace{-4mm}
	%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
  	%	\item MATLAB and R: Multivariate classification and regression
  	%	\item Computational models of visual object recognition
	%\end{itemize}

	\vspace{-1.5mm}	
         \textbf{Ph.D. in Neurosciences}, Université de Toulouse, CNRS, France \hfill \textbf{2010}\\
	Highest academic distinction: Très honorable avec les félicitations du jury à l'unanimité.\\
	\textsl{Eyetracking, analysis of behavioral data, models of ultra-fast reaction times}
	
	\vspace{-1.5mm}
	\textbf{Master in Cognitive Science}, ENS / EHESS / X / Paris 5-6, France  \hfill \textbf{2006}\\
	\textsl{Graduated magna cum laude}
	
	\vspace{-1.5mm}
	For a full list of my scientific achievements, please see my \href{http://scrouzet.github.io/cv/CVSebastienCrouzet.pdf}{academic CV}.


%\newpage

    \vspace{3mm}
    \section{\mysidestyle Skills}
    \vspace{-0.5mm}

	\paragraph{Generic}
	\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt \leftmargin=0em \itemindent=-1.5em
  		\item Active team member in collaborative projects with interdisciplinary scientists worldwide.
  		\item Outstanding organizational and analytical skills, able to assess needs and develop creative solutions. 
  		\item Goal-driven and highly motivated to complete ambitious projects.
  		\item Effective and accurate in background research and follow-up of the literature in several active fields.
  		\item Ability to learn and apply new techniques rapidly and independently.
	\end{itemize}

	\paragraph{Data Analysis}
	\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt \leftmargin=0em \itemindent=-1.5em
  	\item Analyzed behavioral, electrophysiological (EEG and iEEG) and eye movement data.
	\item Simulated behavioral and neuronal data using computational models.
	\end{itemize}
		
	\paragraph{Communication}
	\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt \leftmargin=0em \itemindent=-1.5em
  		\item Distinct teaching skills (>200h), consistently received excellent student and supervisor ratings.
  		\item Proficient in conveying complex models and original findings to professionals.
  		\item Excellent ability to write and transform technical data into interesting, informative reading.
  		\item Strong interest in information and data vizualization (\href{http://www.edwardtufte.com/tufte/}{Tufte} enthusiast).
  		\item Presented results at world-class scientific conferences in Europe and United States.
	\end{itemize}
	
	\paragraph{Organization and management}
	\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt \leftmargin=0em \itemindent=-1.5em
  		\item Founder of the \href{http://incognu.fr/}{inCOGnu} local association for cognitive science outreach.
  		\item Led the organization of the CJCSC'09 (>100 participants) $\rightarrow$ management of a team of 15 people.
	\end{itemize}

		
\newpage

\vspace{3mm}
% Technical Skills
    \section{\mysidestyle Technical\\Skills}

	\textsl{Operating Systems}: Advanced knowledge of Mac OS and GNU Linux.\\
	\textsl{Programming languages}: \\
		\phantom{1em} \textsl{Matlab}: Data analysis, machine learning and computer vision.\\
		\phantom{1em} \textsl{R}: Split-Apply-Combine Strategy with plyr and reshape2, ggplot2, knitr.\\
		\phantom{1em} \textsl{Python}: SciPy, NumPy, scikit-learn.\\
	\textsl{Eye movement recording}: SR Research Eyelink, SMI View Eyetracker, Chronos Eyetracker, EOG.\\
	\textsl{EEG and iEEG analysis}: Homemade MATLAB functions and EEGlab MATLAB toolbox.\\
	\textsl{Statistical Analysis}: Machine learning, multivariate statistics, parametric and non-parametric tests, bootstrapping and permutation methods, \\
	\textsl{Communication and publishing}: Advanced knowledge of \LaTeX, Adobe Illustrator, Keynote, and HTML/CSS.



%    \vspace{3mm}
%    \section{\mysidestyle Specialties}
%	statistics, data analysis, research,  information visualization, programming (R and Matlab), teaching, writing, presentations, public speaking


\vspace{3mm}
    \section{\mysidestyle Languages}
	\textsl{French}: Mother tongue\\
	\textsl{English}: Fluent\\
	\textsl{Spanish}: Elementary

    % Personal information
    \section{\mysidestyle Civil\\Status}
    31 years old, French, married, one daughter.	

\vspace{3mm}	
%% Referees
	\section{\mysidestyle Referees} 

	\textbf{Dr Simon J. Thorpe}, CNRS, Toulouse, France  \hfill \textsl{\href{mailto:simon.thorpe@cerco.ups-tlse.fr}{simon.thorpe@cerco.ups-tlse.fr}}\\
	\textbf{Dr Thomas Serre}, Brown University, Providence, RI, USA \hfill \textsl{\href{mailto:thomas_serre@brown.edu}{thomas\_serre@brown.edu}} \\
	\textbf{Dr Niko A. Busch}, Charité University, Berlin, Germany \hfill \textsl{\href{mailto:niko.busch@charite.de}{niko.busch@charite.de}} \\

\end{resume}
\end{document}
